TODO: A Survey of StarCraft AI Techniques

### 2012-08-15 survey.tex
Some more work on the open problems section

@@

@@

{\color{blue}
[This is a preliminary list of open questions, derived from the Skype call on July 19. Some work is still required to turn this into the final list]

There are a set of problems that are either solved in RTS games (path-finding), or for which we have very good solutions (micro management). But there are features that are not exhibited by any of the current Starcraft playing bots. For example, current bots are incapable of coming up on their own with tactical moves such as unit drops. Some bots do drops, but only if this is hard-coded; no bot has the capability of reasoning about all the possible moves available, and discovering that doing a drop is the best thing to do right now. This is related to the lack of real-time adversarial planning techniques that scale up to RTS games. Similarly, current bots do not exhibit adaptation to opponent strategies. Some switch between different build-orders, but do not fully adapt their strategy. No bot is capable of observing the opponent and autonomously come up with a good plan (from scratch) to counter the opponent strategy.

In general, this is a list of open problems:

\begin{itemize}
\item Adaptation to opponent
\item Learning (from opponent, from traces or from mistakes)
\item Scalability: this includes:
\begin{itemize}
\item a) how to scale up existing algorithms for adversarial domains like game tree search or others, and 
\item b) multi-scale planning/reasoning, how to integrate control, tactics and strategy together (e.g. how to interface them).
\end{itemize}
\item Adversarial real-time planning and scheduling under uncertainty with resources: this basically includes three general unsolved AI problems:
\begin{itemize}
\item Adversarial planning under real-time constraints (there is some work on this area to be presented this year in AIIDE)
\item Adversarial planning under uncertainty 
\item Planning with resources (there exist planning algorithms that handle resources, like GRT-R, but cannot scale up to the size of problems needed for e.g. Starcraft)
\end{itemize}
\item How to exploit and incorporate domain knowledge: we know how to incorporate some aspects of domain knowledge (e.g. build orders), but, in general, how to incorporate some forms of domain knowledge into algorithms for RTS games is still an open problem. For example, standard techniques to encode strategies for other forms of games, like Behavior Trees, are hard to deploy in RTS games. 
\end{itemize}
}

>>>>

{\color{blue} [Here, a brief overview of RTS games, which are their main characteristics, etc.]}

@@

\subsection{Holistic Approaches}

{\color{red} [Santi: some RTS AI techniques attempt to address the problem in a holistic way, for example the Darmok system, is there enough work on this for justifying a whole subsection? or should we just spread the few pieces of work on this over the previous sections].}

@@

{\color{blue}
[This is a preliminary list of open questions, derived from the Skype call on July 19. Some work is still required to turn this into the final list]
}

As illustrated in this paper, there is a set of problems in RTS game AI that could be considered mostly solved, of for which we have very good solutions. One example of such problems is pathfinding (mostly solved) or micro-management (we have good solutions).

However, there are many other problems for which this is not the case. For example, there is no current Starcraft bot that can come up with its own tactical moves, such as ``unit drops''. Some bots do drops, but only if this is hard-coded; no bot has the capability of reasoning about the current situation, synthesize a tactical move that involves a ``unit drop'', and determine that this move is the best one in the current situation. This is related to the lack of real-time adversarial planning techniques that scale up to the size required for RTS games. Similarly, current bots do not exhibit adaptation to opponent strategies. Some switch between different build-orders, but do not fully adapt their strategy. No bot is capable of observing the opponent and autonomously synthesize a good plan from scratch to counter the opponent strategy.

Specifically, the list of problems that are currently unsolved, grouped in various categories:

{\color{blue}

\begin{itemize}

\item Learning and adaptation:
\begin{itemize}
\item Adaptation to opponent strategy.
\item Learning from experience in RTS games.
\item Learning from observation (from demonstration, or from observing the opponent) in RTS games.
\end{itemize}

\item Planning:
\begin{itemize}
\item Adversarial planning under real-time constraints (there is some work on this area to be presented this year in AIIDE).
\item Adversarial planning under uncertainty.
\item Adversarial planning in partially-observable domains.
\item Adversarial planning with resources (there exist planning algorithms that handle resources, like GRT-R, but cannot scale up to the size of problems needed for e.g. Starcraft).
\end{itemize}

\item Scalability:
\begin{itemize}
\item How to scale up existing algorithms for adversarial domains like game tree search or Monte Carlo search to the very large dimensions of RTS games.
\end{itemize}

\item Integration:
\begin{itemize}
\item Multi-scale planning/reasoning: how to integrate reasoning at multiple levels of abstraction.
\end{itemize}

\item Domain Knowledge: 
\begin{itemize}
\item we know how to incorporate some aspects of domain knowledge (e.g. build orders), but, in general, how to incorporate some forms of domain knowledge into algorithms for RTS games is still an open problem. For example, standard techniques to encode strategies for other forms of games, like Behavior Trees, are hard to deploy in RTS games. 
\end{itemize}
\end{itemize}
}
